\documentclass[12pt,fleqn,a4paper,oneside]{mybook} %Final!!!
%\documentclass[11pt,fleqn,a4paper,draft]{mybook} %DRAFT - highlights overflow, leaves out images

%\usepackage{microtype}
\usepackage[slovak]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{mathtools}  					
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{etoolbox}
\usepackage[table,xcdraw]{xcolor}                       %Problematic URL in reference
\apptocmd{\sloppy}{\hbadness 10000\relax}{}{}%Removes badness warnings
%This is to remove warnings resulting by otherwise OK URL's
\usepackage[hyphens]{url}
\usepackage{notes}

\usepackage{svg}
\usepackage{gensymb}

%This custom command defines how the literal menus look like.
\newcommand{\gui}[1]{{\emph{#1}}} %Gui commands, icon names, buttons
% All code, functions, variables are typed like this
\newcommand{\code}[1]{{\lstinline[columns=fixed]{#1}}}

\newcommand{\angl}[1]{{\footnote{\emph{angl.}\ {#1}}}} %Shorthand english equivalent


\usepackage[left=35mm,right=35mm,top=25mm,bottom=25mm,paperwidth=210mm,paperheight=297mm,includehead]{geometry}
\linespread{1}

\usepackage{titlesec}
\titleformat{\chapter}[hang]{\normalfont\huge\bfseries}{\thechapter}{1em}{}


\DeclarePairedDelimiter{\diagpars}{(}{)}
\newcommand{\diag}{\operatorname{diag}\diagpars}

\let\oldhat\hat
\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
%\renewcommand{\hat}[1]{\oldhat{\boldsymbol{\mathbf{#1}}}}


\usepackage{amsthm}
\usepackage{etoolbox}% http://ctan.org/pkg/etoolbo
\theoremstyle{definition}
\newtheorem{exmp}{Pr\'{i}klad}[chapter]
\AtEndEnvironment{exmp}{\null\hfill\qedsymbol}

\usepackage{listings,color} 			    %To list Matlab code
\definecolor{mygrey}{gray}{0.5}	        %Define a gray color
\lstset{
	basicstyle=\ttfamily,
	numbers=none,
	commentstyle=\color{mygrey},
	breaklines=true,
}
%extended Matlab language
\lstdefinelanguage{exMatlab}[]{Matlab}      %Defining expanded Matlab
{morekeywords={rng,pyulear,plot,hold,randn,filter,length,abs,periodogram,fft,sin,randn,xcorr,fminsearch,dlqr,predmodelqp,dlyap,ones,linprog,quadprog,optimset,qpOASES,qpOASES_sequence,sysStruct,probStruct,mpt_control,volume,hull,extreme,mpt_exportc,mpt_getInput,sdpvar,blkdiag,sdpsettings,solvesdp,geomean,double},
	sensitive=true,
	alsoletter={_}
}



\pagestyle{empty}

\begin{document}
	%%%%%%% Zaciaatok %%%%%%%%
	\input{Obalka}
	\input{Titul}
	\input{Zadanie}
	\input{Prehlasenie}
	\input{Podakovanie}
	\input{Abstrakt}
	\tableofcontents
	\thispagestyle{empty}
	\cleardoublepage
	
	%%%%%% Jednotlive kapitoly %%%%%%%%%
	\pagestyle{plain}
	\pagenumbering{arabic}
	\setcounter{page}{1}
	
	\include{Uvod}
	\include{Kapitola1}
	\include{Kapitola2}
	\include{Kapitola3}
	%[...]
	\include{Zaver}
	
	%%%%%%% Koniec %%%%%%%%
	\bibliographystyle{abbrv}
	\addcontentsline{toc}{chapter}{Literat\'{u}ra}
	\bibliography{bibliog.bib}
	
	\begin{thebibliography}{10}
	\bibitem{VL6180X}
	\textbf{STMicroelectronics}, \textit{VL6180X - Proximity and ambient light sensing module} [online], 2016, [cit 2022-4-21] Dostupné z: \url{https://www.st.com/resource/en/datasheet/vl6180x.pdf } 
	
	\bibitem{MPU6050}
	\textbf{InvenSense Inc.}, \textit{MPU-6000 and MPU-6050 Product Specification Revision 3.4} [online], 2013 [cit. 2022-4-21] Dostupné z:
	\url{https://invensense.tdk.com/wp-content/uploads/2015/02/MPU-6000-Datasheet1.pdf}
	
	\bibitem{LDO}
	\textbf{STMicroelectronics}, \textit{ST732 Datasheet} [online], 2021 [cit. 2022-4-28] Dostupné z:
	\url{https://www.mouser.sk/ProductDetail/STMicroelectronics/ST732M28R?qs=MLItCLRbWsxtXiiWQqtIMw%3D%3D}
	
	\bibitem{Anicka}
	\textbf{A. Vargová}, \textit{BoBShield: a miniature "ball on beam" experiment}, Slovenská technická univerzita v Bratislave, Strojnícka fakulta, 2021, Bratislava, Slovenská republika
	
	
	\bibitem{BOBexperiment}
	\textbf{CTMS - Control tutorials for MATLAB and SIMULINK}, \textit{Ball and Beam: System Modeling} [online], [cit. 2022-5-12] Dostupné z:
	\url{https://github.com/gergelytakacs/AutomationShield/wiki/BoBShield}
	
	
	\bibitem{Autoshield}
	\textbf{G. Takacs}, \textit{BOBShield} [online], [cit. 2022-4-22] Dostupné z:
	\url{https://www.hennlich.sk/fileadmin/user_upload/sk_gufer%C3%A1_-_preh%C4%BEad_profilov.pdf}
	
	
	\bibitem{Servo}
	\textbf{ISL Products International Ltd.}, \textit{Servo Motor Fundamentals} [online]. [cit. 2022-5-20] Dostupné z:
	\url{https://islproducts.com/design-note/servo-motor-fundamentals/}
	
	\bibitem{Servo-stare}
	\textbf{DFROBOT}, \textit{9g Metal Gear Micro Servo (1,8Kg)} [online]. [cit. 2022-4-22] Dostupné z:
	\url{https://www.dfrobot.com/product-1338.html}
	
	\bibitem{Servo-nove}
	\textbf{SAVOX-SERVO}, \textit{Savox - Servo - SH-0253 - Digital - DC - Motor } [online]. [cit. 2022-5-22] Dostupné z:
	\url{https://www.savox-servo.com/Servos-c-1338/Brushed-Motor-c-1340/Savox-Servo-SH-0253-Digital-DC-Motor/}
	
	
	\bibitem{MPUfoto}
	\textbf{MOUSER Electronics}, \textit{MPU-6050} [online]. [cit. 2022-5-12] Dostupné z:
	\url{https://www.mouser.sk/ProductDetail/TDK-InvenSense/MPU-6050?qs=u4fy%2FsgLU9O14B5JgyQFvg%3D%3D}
	
	\bibitem{Priemer}
	\textbf{MathWorks}, \textit{Sliding Window Method and Exponetial Weigthing Method} [online]. [cit. 2022-5-22] Dostupné z:
	\url{https://www.mathworks.com/help/dsp/ug/sliding-window-method-and-exponential-weighting-method.html}
	
	
\end{thebibliography}
\end{document}